Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-05-24 Scripts/Initial_Analysis.Rmd
sd, not mean.-

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    # Alternative method sensitivity analysis
    group_by(taxon_key,neighbour_id,year) %>% #Average historic data per year first
    # group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    summarise_at(vars("trans_index"),
                 c(trend= mean),
                 na.rm=T
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

    taxon <- unique(Raw_Result$taxon_key)
    name_raw <- paste(my_path("R",extra_path = "/Emergence_alt_sens_raw/"),taxon,"_emergence_raw.csv",sep="")

    write_csv(Raw_Result,
              name_raw)

@@

    name <- paste(my_path("R",extra_path = "/Emergence_alt_sens/"),taxon_key,"_emergence.txt",sep="")

>>>>

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    # Alternative method sensitivity analysis
    group_by(taxon_key,neighbour_id,year) %>% #s.d. historic data per year first
    # group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    summarise_at(vars("trans_index"),
                 c(trend = sd),
                 na.rm=T
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

    # taxon <- unique(Raw_Result$taxon_key)
    # name_raw <- paste(my_path("R",extra_path = "/Emergence_alt_sens_raw/"),taxon,"_emergence_raw.csv",sep="")
    # 
    # write_csv(Raw_Result,
    #           name_raw)

@@

    name <- paste(my_path("R",extra_path = "/Emergence_alt_sens_sd/"),taxon_key,"_emergence.txt",sep="")
